This page and the next page should be removed

### 2021-01-16 analysis/manuscript.Rmd
attempt to add evokeds for exp3

# Chunk options
knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)

# Bibliography file
r_refs("analysis/manuscript_files/r-references.bib")

# Create export folder for results
dir.create("analysis/export", showWarnings = FALSE)

# Do we want to run analysis for Experiment 3?
run_exp3 <- FALSE
```

@@

```{r exp1-preparation}
# Define function for reading and formatting behavioral data
read_behav <- function(txt_fname) {
  # Read log file
  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
  # Rename columns for participant and item IDs
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = case_when(
      Wdh %in% c(211, 231) ~ "I",
      Wdh %in% c(212, 232) ~ "II",
      Wdh %in% c(213, 233) ~ "III",
      Wdh == 234 ~ "IV"
    ) %>% as_factor()) %>%
    # Remove filler stimuli (i.e.,well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  excl_known <- dat %>% filter(part == "I" & Tastencode %in% c(201, 251)) %>% pull(item)
  excl_informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  excl_naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  # Create a new condition for the experimental condition
  dat %<>% mutate(condition = case_when(
    item %in% excl_known ~ "Excl_known",
    item %in% excl_informed ~ "Excl_informed",
    item %in% excl_naive ~ "Excl_naive",
    item %in% informed ~ "Informed",
    item %in% naive ~ "Naive"
  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if ("richtig_inv" %in% dat$Bed) {
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    # Return only relevant columns
    dat %<>% select(part, condition, participant, item, RT)
  }
  return(dat)
}

@@

>>>>

# Set global chunk options
knitr::opts_chunk$set(include = FALSE, fig.align = "center", out.width = "100%", fig.width = 10)

# Link to the bibliography file
r_refs("analysis/manuscript_files/r-references.bib")

# Create an export folder for results
dir.create("analysis/export", showWarnings = FALSE)

# Do you want to re-run the EEG preprocessing? Note that this can only be used with the raw EEG data, which are
# available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
rerun_preproc <- FALSE

# Do you want to re-run the linear mixed-effect models? This can be done even if only the preprocessed single-trial
# data are available (from GitHub and/or the OSF). Note, however, that the model fitting may take more than 24 hours.
rerun_models <- FALSE
```

@@

```{r exp1-preparation}
# Define function for reading and formatting the behavioral data
read_behav <- function(txt_fname) {
  # Read the log file
  dat <- suppressWarnings(read_tsv(txt_fname, col_types = cols()))
  # Rename columns for participant and item IDs
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = case_when(
      Wdh %in% c(211, 231) ~ "I",
      Wdh %in% c(212, 232) ~ "II",
      Wdh %in% c(213, 233) ~ "III",
      Wdh == 234 ~ "IV"
    ) %>% as_factor()) %>%
    # Remove filler stimuli (i.e.,well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  excl_known <- dat %>% filter(part == "I" & Tastencode %in% c(201, 251)) %>% pull(item)
  excl_informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & !Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  excl_naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & !Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  informed <- dat %>% filter(part == "II" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  naive <- dat %>% filter(part == "II" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  # Create a new condition for the experimental condition
  dat %<>% mutate(condition = case_when(
    item %in% excl_known ~ "Excl_known",
    item %in% excl_informed ~ "Excl_informed",
    item %in% excl_naive ~ "Excl_naive",
    item %in% informed ~ "Informed",
    item %in% naive ~ "Naive"
  ) %>% factor(levels = c("Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if ("richtig_inv" %in% dat$Bed) {
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    # Return only relevant columns
    dat %<>% select(part, condition, participant, item, RT)
  }
  return(dat)
}

@@

```{python}
# Define function to compute grand averages per condition
def compute_evokeds(epochs):
    evokeds = dict(); evokeds_dat = dict()
    # Each part becomes a dictionary of conditions
    for pt in ["I", "II", "III"]:
        evokeds[pt] = dict(); evokeds_dat[pt] = dict()
        # Each part becomes a dictionary of conditions
        for pos in ["Inverted", "Upright"]:
            evokeds[pt][pos] = dict(); evokeds_dat[pt][pos] = dict()
            # Each condition becomes a list of participants
            for cn in ["Informed", "Naive"]:
                evokeds[pt][pos][cn] = list(); evokeds_dat[pt][pos][cn] = list()
                # For every participant we average trials separately for all parts and conditions
                for vp in epochs.metadata["participant"].unique():
                    query = 'participant == "' + vp + '" and part == "' + pt + '" and position == "' + pos + '" and condition == "' + cn + '"'
                    evokeds[pt][pos][cn].append(epochs[query].average())
                # Compute grand averages across participants for this part and condition
                evokeds[pt][pos][cn] = mne.grand_average(evokeds[pt][pos][cn])
                # Export only the actual data for R
                evokeds_dat[pt][pos][cn] = evokeds[pt][pos][cn].data
    return (evokeds, evokeds_dat)

# Compute grand averages for Experiment 1
evokeds_exp3, evokeds_dat_exp3 = compute_evokeds_3(epochs=epochs_exp3)
```

```{r}
evokeds_exp3 <- py$evokeds_exp3_anova

compute_erps <- function(evokeds, els, name, start, stop, roi) {
  map(evokeds, function(part){
    map(part, function(position) {
      map(position, function(condition) {
        map_dbl(condition, function(participant) {
          participant[which(els %in% roi), which(times %in% start:stop)] %>% mean()
        })
      }) %>% 
        bind_rows(.id = "condition") %>%
        mutate(participant = factor(1:24)) %>%
        pivot_longer(cols = c("Informed", "Naive"), names_to = "condition", values_to = "amplitude")
    }) %>% bind_rows(.id = "position")
  }) %>% bind_rows(.id = "part")
}
```
